---
title: "DS202LabHW1"
author: "Hanying Shen"
date: "9/5/2019"
output: html_document
---
Hanying Shen, GitHub username: hshen0422
new file upload, commit ID:bc15493c0504e0e14b93a44f29e886358343ab95
Yes, I am able to do so without error. 
My partner and I had a difficult time when we were trying to use Git push to Git Hub. It always shows ! [rejected]        master -> master (non-fast-forward) error: failed to push some refs to 'https://github.com/jessiehwang/ds202_lab1.git' 

2.1 Git is a tool to manage your source code history, and Git manages the evolution of a set of files – called a repository; and GitHub is a hosting service for projects that use Git.

2.2 Yes, they can be used independently. We don't normally do so because they are designed to work together. GitHub is a platform that is built on top of Git to give teams another level of project organization, which includes issue tracking, code reviewing, and much more.

2.3 A repository is the evolution of a set of files. It is like a folder for the project. 

3.1
```{r}
X = c(47,34,33,65,37,NA,43,NA,11,NA,23,NA)
sum(is.na(X)==TRUE)
```
3.2
```{r}
age = c(25,30,45,60,12,41)
smoker = c('T','F','T','F','F','F')
weight = c(120,137,0,168,91,142)
example_data = data.frame(age,smoker,weight)
example_data
example_data[3,3] <-150
example_data
```
3.3
```{r}
# vector with missing data
x <- c(1:4, NA, 6,7, NA)
x
average<-function(x){
  a<-x /sum(x, na.rm = TRUE)
  print(paste("The mean for the variable in the list is",a))
}

avgmean<-function(x) {
  b<-mean(is.na(x))
  print(paste("The mean of 1(for TRUE) and 0(for FALSE) is ",b))
}
average(x)
avgmean(x)

```

3.4
```{r}
both_na <- function(x, y) {
  stopifnot(length(x) == length(y))
  which(is.na(x) & is.na(y))
}

y <- c(1:4, NA, 6,7, NA)
both_na(x,y)
  
```
abdc

